### 2013-02-13 exam5/1.tex
fix a bunch of bugs in solutions

\begin{verbatim}
;; A Set is one of:
;; - (new empty%)
;; - (new singelton% Number)
;; - (new union% Set Set)
;; Interpretation: a set that contains all the *unique* numbers in the data
;; and implements
;; - sum : -> Number
;;   Produce the sum of all the unique elements of this set
;; - sum/acc : Set -> Number
;;   Produce the sum of all the unique elements of this set that are
;;   *not* in the given set
;; - contains? : Number -> Boolean
;;   Does this set contain the given number?
;; - union : Set -> Set
;;   Combine this set with the given set

@@

(define-class singleton%
  (fields n)
  (define (sum) n)
  (define (sum/acc s) (cond [(s . contains? (this . n)) 0]
                            [else (this . n)])))

@@

Unfortunately, as you can see, Van Horn fell asleep before finishing,
and the deadline is today.  Help him out by implementing the
\verb|union| and \verb|contains?| methods for all \verb|Set|s.

\ifrubric
\begin{alltt}
\rubricpts{1 pt -- union method}
\rubricpts{3 pts -- contains method}
;; in empty%
(define (union s) s)
(define (contains n) #f)
;; also ok:
(define (union s) (new union% this s)
;; in singleton%
(define (union s) (new union% this s)
(define (contains n) (= n (this . n)))
;; in union%
(define (union s) (new union% this s)
(define (contains n) (or (this . l . contains n)
                         (this . r . contains n)))
(define e (new empty%))
\rubricpts{2 pts -- tests}
(check-expect (e . contains 5) #f)
(check-expect ((new singleton% 5) . contains 5) #t)
(check-expect ((new singleton% 6) . contains 5) #f)
(check-expect ((new singleton% 6) . union  e . contains 5) #f)
(check-expect (e . union (new singleton% 5) . contains 5) #t)
(check-expect ((new singleton% 5) . union (new singleton% 5) . contains 5) #t)
\end{alltt}
\else
\newpage
[Here is some more space for the previous problem.]
\fi
\newpage

@@

\begin{solution}
\begin{alltt}
\rubricpts{1 pt -- contract & purpose}
;; union-sum : Set Set -> Boolean
\rubricpts{3 pts -- code}
(define (union-contains s1 s2 n)
  (check-expect (s1 . union s2 . sum)
                (+ (s1 . sum) (s2 . sum))))w

>>>>

\begin{verbatim}
;; A Set is one of:
;; - (new empty%)
;; - (new singelton% Number)
;; - (new union% Set Set)
;; Interpretation: a set that contains all the *unique* numbers in the data
;; and implements
;; - sum : -> Number
;;   Produce the sum of all the unique elements of this set
;; - sum/acc : Set -> Number
;;   Produce the sum of all the unique elements of this set that are
;;   *not* in the given set
;; - contains : Number -> Boolean
;;   Does this set contain the given number?
;; - union : Set -> Set
;;   Combine this set with the given set

@@

(define-class singleton%
  (fields n)
  (define (sum) (this . n))
  (define (sum/acc s) (cond [(s . contains (this . n)) 0]
                            [else (this . n)])))

@@

Unfortunately, as you can see, Van Horn fell asleep before finishing,
and the deadline is today.  Help him out by implementing the
\verb|union| and \verb|contains| methods for all \verb|Set|s.

\ifrubric
\begin{alltt}
\rubricpts{1 pt -- union method}
\rubricpts{3 pts -- contains method}
;; in empty%
(define (union s) s)
(define (contains n) #f)
;; also ok:
(define (union s) (new union% this s))
;; in singleton%
(define (union s) (new union% this s))
(define (contains n) (= n (this . n)))
;; in union%
(define (union s) (new union% this s))
(define (contains n) (or (this . l . contains n)
                         (this . r . contains n)))
(define e (new empty%))
\rubricpts{2 pts -- tests}
(check-expect (e . contains 5) #f)
(check-expect ((new singleton% 5) . contains 5) #t)
(check-expect ((new singleton% 6) . contains 5) #f)
(check-expect ((new singleton% 6) . union  e . contains 5) #f)
(check-expect (e . union (new singleton% 5) . contains 5) #t)
(check-expect ((new singleton% 5) . union (new singleton% 5) . contains 5) #t)
\end{alltt}
\else
\newpage
[Here is some more space for the previous problem.]
\fi
\newpage

@@

\begin{solution}
\begin{alltt}
\rubricpts{1 pt -- contract & purpose}
;; union-sum : Set Set -> Boolean
\rubricpts{3 pts -- code}
(define (union-sum s1 s2 n)
  (check-expect (s1 . union s2 . sum)
                (+ (s1 . sum) (s2 . sum))))
